Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-07-25 main_paper.tex
First pass on Abstract and Introduction changing language to accommodate the new Wild bootstrap and Kernel setup.

\begin{abstract}\noindent
  This paper develops a novel bootstrap procedure to obtain robust
  bias-corrected confidence intervals in regression discontinuity (RD) designs
  using the uniform kernel. The procedure uses a residual bootstrap from a
  second order local polynomial to estimate the bias of the local linear RD
  estimator; the bias is then subtracted from the original estimator. The
  bias-corrected estimator is then bootstrapped itself to generate valid
  confidence intervals. The confidence intervals generated by this procedure
  are valid under conditions similar to Calonico, Cattaneo and Titiunik's
  (2014, \textit{Econometrica}) analytical correction---i.e.  when the bias of
  the naive regression discontinuity estimator would otherwise prevent valid
  inference. This paper also provides simulation evidence that our method is
  as accurate as the analytical corrections and we demonstrate its use through
  a reanalysis of Ludwig and Miller's (2008) Head Start dataset.
\end{abstract}

\section{Introduction}
Regression Discontinuity (RD) designs have emerged in the last decade as an
important and popular research design strategy for analyzing the causal impact
of policies and interventions in several fields of the social sciences,
including economics, political science, public policy, and sociology.  This
research strategy exploits the fact that many programs use a threshold based
on a numeric score to determine whether or not to provide a
treatment.\footnote{%
  This score is often referred to as the \textit{running variable} in this
  literature.} %
In its basic version, \textit{sharp RD}, individuals or groups with score
above the threshold are treated while those below the threshold are left
untreated. The identification of the treatment effect at the threshold is then
based on comparing treated and untreated units at the cutoff. When a subject's
position just above or below the cutoff is credibly not related to unobserved
characteristics that would affect the outcome of interest, differences between
treated and untreated individuals at the cutoff can be plausibly attributed to
the treatment alone. As a practical matter this involves comparing units
within a bandwidth just above and just below the threshold. Other RD
strategies exist that can exploit different forms of discontinuities as well.

@@

Our approach exploits CCT's theoretical insight through a new residual
bootstrap. In particular, we propose estimating the local linear model as usual,
then estimating a local second order polynomial and generating bootstrap
datasets by resampling the residuals of that polynomial. Since the second order
polynomial is the true Data Generating Process (DGP) for the bootstrapped data,
its estimate of the treatment effect is the true value of the treatment effect
under the distribution induced by this bootstrap. The bias of the linear model
is therefore known
under this distribution and can be calculated by averaging the error of the
linear model's estimates across many bootstrap replications. This approach is
described in detail by our Algorithm~\ref{Alg1} and the resulting bias corrected
estimator is shown to be asymptotically normal with mean zero in our
Theorem~\ref{T1} under AMSE-optimal bandwidth rates.

Just as in CCT, our bias correction step introduces additional
variability. However, the second order polynomial again adequately estimates the
features of the true DGP that are necessary for estimating and accommodating that
additional variability. So we propose
an iterated bootstrap procedure \citep{hall1988}: use the second order
polynomial residual bootstrap to produce many bootstrap replications of the bias
corrected estimator, and then use the resulting bootstrap distribution to
produce confidence intervals. This procedure, which requires bootstrapping the
datasets produced by an initial bootstrap, is described in Algorithm~\ref{Alg2}, and the resulting confidence intervals are shown to be asymptotically valid in Theorem~\ref{T2}.

The methods presented in this paper are intended as a ``proof of concept'' that
demonstrates that the analytical correction proposed by CCT can also be
implemented through a new bootstrap procedure. We believe that this procedure is
promising because it can allow applied researchers to construct
accurate confidence intervals in settings where unusual forms of dependence
would make it difficult to derive CCT's analytical correction---the dependence
can be accommodated in principle by modifying the resampling algorithm to one
that matches the dependence in the dataset. The specific version of the bootstrap
presented in this paper, however, does not achieve that level of generality yet,
and a limitation should be noted in particular. The confidence
intervals produced by this bootstrap depend on two separate bandwidth parameters
that must be generated elsewhere. Since these bandwidths are generated using
analytical methods, the confidence intervals could easily be produced using the
same methods. Moreover, in this paper we focus on the baseline case of
sharp RD with a local linear model, however, the results and procedures can be easily extended to the general local polynomial
and higher order derivatives (e.g., "Regression Kink Designs) cases.

>>>>

\begin{abstract}\noindent
  This paper develops a novel bootstrap procedure to obtain robust
  bias-corrected confidence intervals in regression discontinuity (RD) designs. The procedure uses a wild bootstrap from a
  second order local polynomial to estimate the bias of the local linear RD
  estimator; the bias is then subtracted from the original estimator. The
  bias-corrected estimator is then bootstrapped itself to generate valid
  confidence intervals. The confidence intervals generated by this procedure
  are valid under conditions similar to Calonico, Cattaneo and Titiunik's
  (2014, \textit{Econometrica}) analytical correction---i.e.  when the bias of
  the naive regression discontinuity estimator would otherwise prevent valid
  inference. This paper also provides simulation evidence that our method is
  as accurate as the analytical corrections and we demonstrate its use through
  a reanalysis of Ludwig and Miller's (2008) Head Start dataset.
\end{abstract}

\section{Introduction}
Regression Discontinuity (RD) designs have emerged in the last decade as an
important and popular research design strategy for analyzing the causal impact
of policies and interventions in several fields of the social sciences,
including economics, political science, public policy, and sociology.  This
research strategy exploits the fact that many programs use a threshold based
on a numeric score to determine whether or not to provide a
treatment.\footnote{This score is often referred to as the \textit{running variable} in this
  literature.}
In its basic version, \textit{sharp RD}, individuals or groups with score
above the threshold are treated while those below the threshold are left
untreated. The identification of the treatment effect at the threshold is then
based on comparing treated and untreated units at the cutoff. When a subject's
position just above or below the cutoff is credibly not related to unobserved
characteristics that would affect the outcome of interest, differences between
treated and untreated individuals at the cutoff can be plausibly attributed to
the treatment alone. As a practical matter this involves comparing units
within a bandwidth just above and just below the threshold. Other RD
strategies exist that can exploit different forms of discontinuities as well.

@@

Our approach exploits CCT's theoretical insight through a new wild
bootstrap. In particular, we propose estimating the local linear model as usual,
then estimating a local second order polynomial and generating bootstrap
datasets based on the approximation provided by that polynomial. Since the second order
polynomial is the true Data Generating Process (DGP) for the bootstrapped data,
its estimate of the treatment effect is the true value of the treatment effect
under the distribution induced by this bootstrap. The bias of the linear model
is therefore known
under this distribution and can be calculated by averaging the error of the
linear model's estimates across many bootstrap replications. This approach is
described in detail by our Algorithm~\ref{Alg1} and the resulting bias corrected
estimator is shown to be asymptotically normal with mean zero in our
Theorem~\ref{T1} under AMSE-optimal bandwidth rates.

Just as in CCT, our bias correction step introduces additional
variability. However, the second order polynomial again adequately estimates the
features of the true DGP that are necessary for estimating and accommodating that
additional variability. So we propose
an iterated bootstrap procedure \citep{hall1988}: use the second order
polynomial wild bootstrap to produce many bootstrap replications of the bias
corrected estimator, and then use the resulting bootstrap distribution to
produce confidence intervals. This procedure, which requires bootstrapping the
datasets produced by an initial bootstrap, is described in Algorithm~\ref{Alg2}, and the resulting confidence intervals are shown to be asymptotically valid in Theorem~\ref{T2}.

The methods presented in this paper are intended as a ``proof of concept'' that
demonstrates that the analytical correction proposed by CCT can also be
implemented through a new bootstrap procedure. We believe that this procedure is
promising because it can allow applied researchers to construct
accurate confidence intervals in settings where unusual forms of dependence
would make it difficult to derive CCT's analytical correction---the dependence
can be accommodated in principle by modifying the resampling algorithm to one
that matches the dependence in the dataset. The specific version of the bootstrap
presented in this paper, however, does not achieve that level of generality yet,
and a limitation should be noted in particular. The confidence
intervals produced by this bootstrap depend on two separate bandwidth parameters
that must be generated elsewhere. Since these bandwidths are generated using
analytical methods, the confidence intervals could easily be produced using the
same methods. Moreover, in this paper we focus on the baseline case of
sharp RD with a local linear model, however, the results and procedures can be easily extended to the general local polynomial
and higher order derivatives cases (e.g., Regression Kink Designs).
